### 2024-01-02 documentation/thesis/thesis_document.tex
more thesis

As it is possible to connect many identical sensors to one host using
the \passthrough{\lstinline!network proxy!}, it must be possible to
address them separately. This separation is done by the
\passthrough{\lstinline!MRPProxy.proxy!} module and is therefore not
part of the core \gls{mrp} library.

@@

The \passthrough{\lstinline!network proxy!} instance pretends to be a
sensor to the \gls{mrp} host, so the multiple sensors must be combined
into one. This is done in several steps, in the
\passthrough{\lstinline!network proxy!} start procedure:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Construct the Sensor ID LookUp-Table}
\item
  \textbf{Merging the sensor capabilities}
\item
  \textbf{Dynamic extension of the available network proxy commands}
\end{enumerate}

>>>>

As it is possible to connect many identical sensors to one host using
the \passthrough{\lstinline!Network-Proxy!}\ref{network-proxy}, it must
be possible to address them separately. This separation is done by the
\passthrough{\lstinline!MRPProxy.proxy!} module and is therefore not
part of the core \gls{mrp} library.

@@

The \passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} instance
pretends to be a sensor to the \gls{mrp} host, so the multiple sensors
must be combined into one. This is done in several steps, in the
\passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} start
procedure:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Construct the Sensor ID LookUp-Table}
\end{enumerate}

Immediately after starting the
\passthrough{\lstinline!network-proxy!}\ref{network-proxy}, the
\gls{id}s of all locally connected sensors are read out. These are
stored together with the instance of the
\passthrough{\lstinline!MRPHal!} module in a \gls{lut}. This makes it
possible to address a sensor directly using its \gls{id}.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  \textbf{Merging the sensor capabilities}
\end{enumerate}

\begin{longtable}[]{@{}llll@{}}
\caption{Sensor capabilities merging
\label{Sensor_capabilities_merging.csv}}\tabularnewline
\toprule
SENSOR A & SENSOR B & MERGED CAPABILITIES & CAPABLE SENSORS ID
LUT\tabularnewline
\midrule
\endfirsthead
\toprule
SENSOR A & SENSOR B & MERGED CAPABILITIES & CAPABLE SENSORS ID
LUT\tabularnewline
\midrule
\endhead
static & & static & A\tabularnewline
& dynamic & dynamic & B\tabularnewline
axis\_temp & axis\_temp & axis\_temp & A B\tabularnewline
axis\_x & axis\_x & axis\_x & A B\tabularnewline
\bottomrule
\end{longtable}

When using sensors with different capabilites, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \passthrough{\lstinline!info!}
command of each sensor is queried. This information is added to the
previously created \gls{lut}. Duplicate entries are summarized (see
Table:\ref{Sensor_capabilities_merging.csv}) and returned to the host
when the \passthrough{\lstinline!info!}\ref{lst:mtsc} command is
received over network.

\begin{lstlisting}[language=bash, caption={MRPproxy REST enpoiint query examples}, label=lst:mtsc]
  # QUERY Network-Proxy capabilities
  $ wget http://proxyinstance.local:5556/proxy/status
  {"capabilities":[
  "static",
  "dynamic",
  "axis_temp",
  "axis_x"
  ]}
\end{lstlisting}

The same procedure is performed for the
\passthrough{\lstinline!commands!} \gls{cli}-command of each sensor, to
merge to available commands of connected sensors into the \gls{lut}.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  \textbf{Dynamic extension of the available network proxy commands} In
  order for the host to be able to send a command to the network
  multi-sensor setup, the command received must be forwarded to the
  correct sensor. In addition, there are commands such as the previously
  used \passthrough{\lstinline!info!} or
  \passthrough{\lstinline!status!} command, which must be intercepted by
  the \passthrough{\lstinline!MRPProxy!} module so that it can be
  handled differently (see example \ref{lst:mtsc}).
\end{enumerate}

To realize this, a \gls{lut} was created in the previous steps, which
contains information regarding
\passthrough{\lstinline!requested capability!} -\textgreater{}
\passthrough{\lstinline!sensor!}-\gls{id} -\textgreater{}
\passthrough{\lstinline!physical sensor!} and allows the commands to be
routed.

For commands where there are several entries for
\passthrough{\lstinline!CAPABLE SENSORS ID LUT!}\ref{Sensor_capabilities_merging.csv},
there are two possible approaches to how the command is processed:

\begin{itemize}
\tightlist
\item
  redirect to each capable sensor
\item
  extend commands using an id parameter
\end{itemize}

These two methods have been implemented and are applied automatically.
The decision is based on which hardware sensors are connected. In a
setup where only the same sensor variants are connected,
\passthrough{\lstinline!redirect to each capable sensor!} is applied.
This offers a time advantage as fewer commands need to be sent from the
host. Thus, with a \passthrough{\lstinline!readsensor!} command, all
sensors are read out via one command and the summarized result is
transmitted to the host.

The \passthrough{\lstinline!extend commands using an id parameter!}
strategy is used for different sensors. Each command is extended on the
\passthrough{\lstinline!network-proxy!}\ref{network-proxy} by another
\gls{id} parameter, according to the following scheme:

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!readsensor <axis> <sensor number>!}-\textgreater{}
  \passthrough{\lstinline!readsensor <axis> <ID>!}
\item
  \passthrough{\lstinline!opmode!}-\textgreater{}
  \passthrough{\lstinline!opmode <ID>!}
\end{itemize}

This allows the host to address individual sensors directly via their
specific \gls{id}.
